fdcoexist

### 2018-08-23 paper_simulations.Rmd
:sparkles: Plot trait variance along envtal gradient

# Synthetic plot

@@

>>>>

# Synthetic plots

@@

```{r plot_trait_var_env}
all_trait_var = all_df %>%
    filter(N > 0) %>%
    group_by(env_width, compet_status, cor_level, scenario, patch) %>%
    summarise_at(vars(matches("trait[123]$")), funs(var = var(.))) %>%
    ungroup() %>%
    mutate(patch_optim = as.numeric(gsub("patches", "", patch))) %>%
    gather("trait_name", "trait_value", contains("trait"))

plot_trait_var_env_constant = ggplot(all_trait_var %>%
                                         filter(env_width == "constant"),
                                     aes(patch_optim, trait_value,
                                         color = trait_name,
                                         linetype = compet_status)) +
    geom_line() +
    facet_grid(vars(cor_level), vars(scenario), scales = "free_y",
               labeller = labeller(scenario = label_value,
                                   cor_level = c(no_cor   = "r = 0",
                                    low_cor  = "r = 0.3",
                                    high_cor = "r = 0.7"))) +
    scale_color_discrete(name = "Trait",
                         labels = c(trait1_var = "Trait 1",
                                    trait2_var = "Trait 2",
                                    trait3_var = "Trait 3")) +
    scale_linetype_discrete(name = NULL,
                            labels = c(compet    = "Competition",
                                       no_compet = "No Competition")) +
    labs(x = "Environment",
         y = "Trait Variance",
         subtitle = "Constant Environment") +
    theme(legend.position = "top")

plot_trait_var_env_constant

plot_trait_var_env_varying = ggplot(all_trait_var %>%
                                         filter(env_width == "varying"),
                                     aes(patch_optim, trait_value,
                                         color = trait_name,
                                         linetype = compet_status)) +
    geom_line() +
    facet_grid(vars(cor_level), vars(scenario), scales = "free_y",
               labeller = labeller(scenario = label_value,
                                   cor_level = c(no_cor   = "r = 0",
                                    low_cor  = "r = 0.3",
                                    high_cor = "r = 0.7"))) +
    scale_color_discrete(name = "Trait",
                         labels = c(trait1_var = "Trait 1",
                                    trait2_var = "Trait 2",
                                    trait3_var = "Trait 3")) +
    scale_linetype_discrete(name = NULL,
                            labels = c(compet    = "Competition",
                                       no_compet = "No Competition")) +
    labs(x = "Environment",
         y = "Trait Variance",
         subtitle = "Varying Environment") +
    theme(legend.position = "top")

plot_trait_var_env_varying
```
